---
title: "Week 6 Homework - Introduction to Quarto"
author: "Linnea Nordli"
format: 
  html:
    code-fold: true # code hidden by default, with a toggle button
    code-summary: "Show code" # customize button label 
    mainfont: "Times new roman" # main body text
    fontsize: 12pt # main font size
    fontcolor: black # main font color
    embed-resources: true # avoids the extra folders by placing outputs into the HTML itself 
    toc: true
    toc-depth: 2
    toc-location: right
    toc-title: "Table of Contents"
editor: visual
warning: false
theme: lumen
---

# Create the most beautiful Quarto output using datasheets worked with in class 
Must create *at least* one figure and one table, both need to be **publication ready** and **aesthetically pleasing**. A few things to consider:

- Clear headings, titles, and legends
- Captions for figure and table
- Nice themes

```{r}
#| echo: false
# Load libraries
library(tidyverse)
library(palmerpenguins)
library(kableExtra)
library(here)

# Assign dataset
pengdata <- penguins
```

## Create figure using penguin data from palmerpenguins
```{r}
#| label: fig-bodymass-flipper
#| fig-cap: "A scatterplot depicting body mass vs. flipper length for three penguin species. Color points are grouped by penguin species as shown in the legend on the right. Solid color lines indicate best fit line by linear regressions, with 95% Confidence Intervals shown in the respective shaded areas for each species."
#| fig-align: "center"
#| fig-height: 4
#| fig-width: 6
pengdata |> 
  ggplot(aes(x=body_mass_g, y=flipper_length_mm, color=species))+ # map body mass by flipper length
  geom_point()+ # add individual observations as scatterplot
  geom_smooth(method = lm)+ # add linear regression, with shading of 95% Confidence Intervals 
  labs(x="Body Mass (g)", y="Flipper Length (mm)", color="Species")+ # change axes and legend names
  theme_bw()+
  theme(axis.title = element_text(size = 12))+
  scale_colour_viridis_d()
```


```{r}
#| echo: false
# separately assign to object, when i tried to assign in the code above the figure would not display on HTML file
plot <- pengdata |> 
  ggplot(aes(x=body_mass_g, y=flipper_length_mm, color=species))+ # map body mass by flipper length
  geom_point()+ # add individual observations as scatterplot
  geom_smooth(method = lm)+ # add linear regression, with shading of 95% Confidence Intervals 
  labs(x="Body Mass (g)", y="Flipper Length (mm)", color="Species")+ # change axes and legend names
  theme_bw()+
  theme(axis.title = element_text(size = 12))+
  scale_colour_viridis_d()

ggsave(here("Week_06", "Outputs", "HW_plot_mass_flipper.png"), create.dir = TRUE)
```

## Create table using penguin data from palmerpenguins
```{r}
#| label: tbl-bodymass-flipper
#| tbl-cap: "Mean body mass and flipper length for three penguin species."
pengdata |> 
  group_by(species) |> 
  summarise(BodyMass = mean(body_mass_g, na.rm = TRUE), 
            FlipperLength = mean(flipper_length_mm, na.rm = TRUE)) |> 
  kbl(col.names = c("Species", "Mean body mass (g)", "Mean flipper length (mm)"), align = "ccc") |> 
  kable_classic() |> 
  kable_styling(full_width = FALSE)
```

## Conclusion
As shown in @fig-bodymass-flipper, Gentoo penguins display the largest body mass and longest flippers. @tbl-bodymass-flipper shows the individual values of average body mass and flipper length by the three penguin species.